\documentclass[12pt, titlepage]{article}

\usepackage{amsmath, mathtools}

\usepackage[round]{natbib}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[section]{placeins}
\usepackage{caption}
\usepackage{fullpage}

\hypersetup{
bookmarks=true,     % show bookmarks bar?
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with linkbordercolor)
citecolor=blue,      % color of links to bibliography
filecolor=magenta,  % color of file links
urlcolor=cyan          % color of external links
}

\usepackage{array}

\externaldocument{../../SRS/SRS}

\input{../../Comments}
\input{../../Common}

\begin{document}

\title{Module Interface Specification for \progname{}}

\author{\authname}

\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
01/15/2025 & 0.0 & Revision 0\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

See SRS Documentation at \href{https://github.com/TPGEngine/tpg/blob/main/docs/SRS/SRS.pdf}{this link}. This section records information for easy reference. \\

% \wss{Also add any additional symbols, abbreviations or acronyms}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  AC & Anticipated Change\\
  DAG & Directed Acyclic Graph \\
  DNN & Deep Neural Network \\
  FR & Functional Requirement \\
  M & Module \\
  MG & Module Guide \\
  MIS & Module Interface Specification \\
  Multi-Task RL & Multi-Task Reinforcement Learning \\
  NFR & Non-Functional Requirement \\
  OS & Operating System \\
  R & Requirement\\
  RL & Reinforcment Learning \\
  SC & Scientific Computing \\
  SRS & Software Requirements Specification \\
  TPG & Tangled Program Graphs\\
  UC & Unlikely Change \\
  % \wss{etc.} & \wss{...}\\
  \bottomrule
\end{tabular}\\

\newpage

\tableofcontents

\newpage

\pagenumbering{arabic}

\section{Introduction}

The following document details the Module Interface Specifications for
\wss{Fill in your project name and description}

Complementary documents include the System Requirement Specifications
and Module Guide.  The full documentation and implementation can be
found at \url{...}.  \wss{provide the url for your repo}

\section{Notation}
The structure of the MIS for modules comes from \citet{HoffmanAndStrooper1995},
with the addition that template modules have been adapted from
\cite{GhezziEtAl2003}.  The mathematical notation comes from Chapter 3 of
\citet{HoffmanAndStrooper1995}.  For instance, the symbol := is used for a
multiple assignment statement and conditional rules follow the form $(c_1
\Rightarrow r_1 | c_2 \Rightarrow r_2 | ... | c_n \Rightarrow r_n )$.

The following table summarizes the primitive data types used by TPG. 

\begin{center}
\renewcommand{\arraystretch}{1.2}
\noindent 
\begin{tabular}{l l p{7.5cm}} 
\toprule 
\textbf{Data Type} & \textbf{Notation} & \textbf{Description}\\ 
\midrule
character & char & a single symbol or digit\\
integer & $\mathbb{Z}$ & a number without a fractional component in (-$\infty$, $\infty$) \\
natural number & $\mathbb{N}$ & a number without a fractional component in [1, $\infty$) \\
real & $\mathbb{R}$ & any number in (-$\infty$, $\infty$)\\
\bottomrule
\end{tabular} 
\end{center}

\noindent
The specification of TPG uses some derived data types: sequences, strings, and
tuples. Sequences are lists filled with elements of the same data type. Strings
are sequences of characters. Tuples contain a list of values, potentially of
different types. In addition, TPG uses functions, which
are defined by the data types of their inputs and outputs. Local functions are
described by giving their type signature followed by their specification.

\section{Module Decomposition}

The following table is taken directly from the Module Guide document for this project.

\begin{table}[h!]
  \centering
  \begin{tabular}{p{0.3\textwidth} p{0.6\textwidth}}
  \toprule
  \textbf{Level 1} & \textbf{Level 2}\\
  \midrule
  
  {Hardware-Hiding Module} & N/A \\
  \midrule
  
  \multirow{4}{0.3\textwidth}{Behaviour-Hiding Module} & Classic Control Module \\
  & MuJoCo Module\\
  & Visualization Module\\
  & Logging Module\\
  \midrule
  
  \multirow{2}{0.3\textwidth}{Software Decision Module} & {TPG Experiment Module}\\
  & Framework Module\\
  \bottomrule
  
  \end{tabular}
  \caption{Module Hierarchy}
  \label{TblMH}
  \end{table}

\newpage
~\newpage

\section{MIS of MuJoCo Module} \label{MuJoCo Module}

\subsection{Module}
MujocoEnv

\subsection{Uses}
MuJoCo Framework (mujoco/mujoco.h), Task Environment (TaskEnv.h)

\subsection{Syntax}

\subsubsection{Exported Constants}
None

\subsubsection{Exported Access Programs}
\begin{center}
  \begin{tabular}{p{4cm} p{4cm} p{3cm} p{2cm}}
    \hline
    \textbf{Name} & \textbf{Input} & \textbf{Output} & \textbf{Exceptions} \\
    \hline
    mujocoEnv & - & - & - \\
    \hline
    \texttildelow mujocoEnv & - & - & - \\
    \hline
    reset & \{rng : mt19937\&\} & - & - \\
    \hline
    terminal & - & bool & - \\
    \hline
    sim\_step & \{action : std::vector\textless double\textgreater \}& Results & - \\
    \hline
    initialize\_simulation & - & - & Unable to load binary model \\
    \hline
    set\_state & \{qpos : std::vector\textless double\textgreater,  qvel : std::vector\textless double\textgreater\} & - & - \\
    \hline
    do\_simulation & \{ctrl : std::vector\textless double\textgreater, n\_frames: int\} & - & - \\
    \hline
    GetObsSize & - & int & - \\
    \hline
    \end{tabular}
\end{center}

\subsubsection{State Variables}

\begin{center}
  \begin{tabular}{p{4cm} p{4cm} p{4cm}}
    \hline
    \textbf{Name} & \textbf{Type} & \textbf{Description} \\
    \hline
    m\_ & mjModel* & Pointer to the MuJoCo model\\
    \hline
    d\_ & mjData* & Pointer to the MuJoCo data\\
    \hline
    cam\_ & mjvCamera & Camera used for visualization\\
    \hline
    opt\_ & mjvOption & Visualization options\\
    \hline
    scn\_ & mjvScene & Visualization scene\\
    \hline
    con\_ & mjrContext & Custom GPU rendering context\\
    \hline
    init\_qpos\_ & std::vector<double> & Initial positions\\
    \hline
    init\_qvel\_ & std::vector<double> & Initial velocities\\
    \hline
    model\_path\_ & String & Absolute path to model xml file\\
    \hline
    frame\_skip\_ & Integer & Number of frames per simulation step\\
    \hline
    obs\_size\_ & Integer & Size of the observation space\\
    \hline
  \end{tabular}
\end{center}

\subsubsection{Environment Variables}
None

\subsubsection{Assumptions}
\begin{itemize}
  \item The MuJoCo environment is properly installed on the user's device.
\end{itemize}

\subsubsection{Access Routine Semantics}
\noindent mujocoEnv():
\begin{itemize}
\item output: $out :=$ self
\item exception: none
\end{itemize}
\noindent \texttildelow mujocoEnv():
\begin{itemize}
\item transition: self $\rightarrow$ destroyed
\item exception: none 
\end{itemize}
\noindent reset(\textit{rng}):
\begin{itemize}
\item transition: resets the environment to initial state using a random number generator, \textit{rng}.
\item exception: none
\end{itemize}
\noindent terminal():
\begin{itemize}
\item transition: environment in terminal state ? terminal $:=$ true : terminal $:=$ false
\item output: $out :=$ terminal
\item exception: none
\end{itemize}
\noindent sim\_step(\textit{action}):
\begin{itemize}
\item transition: advances the simulation by one step using the given \textit{action}.
\item output: $out :=$ Results object containing simulation outcomes.
\item exception: none
\end{itemize}
\noindent initialize\_simulation():
\begin{itemize}
\item transition: initializes the simulation by loading the MuJoCo model and creating its data structure.
\item exception: unable to load binary model error.
\end{itemize}
\noindent set\_state(\textit{qpos}, \textit{qvel}):
\begin{itemize}
\item transition: sets the positions and velocities, \textit{qpos} and \textit{qvel}, in the simulation state.
\item exception: none
\end{itemize}
\noindent do\_simulation(\textit{ctrl}, \textit{n\_frames}):
\begin{itemize}
\item transition: executes \textit{n\_frames} of simulation steps with the given control inputs, \textit{ctrl}.
\item exception: none 
\end{itemize}

\subsubsection{Local Functions}
None

\section{MIS of Visualization Module} \label{Visualization Module}

\subsection{Module}
The visualization module implements visualization functionality of a TPG experiment with graphs, charts, video playback, and a realtime simulation.

\subsection{Uses}
The visualization module is used to visualize the results of a TPG experiment while it is running or after the experiemnt has completed. This information contains data pertaining to what is going on in an experiment, and performance metrics.

\subsection{Syntax}

\subsubsection{Exported Constants}
N/A

\subsubsection{Exported Access Programs}
\begin{center}
  \begin{tabular}{p{2cm} p{4cm} p{4cm} p{4cm}}
  \hline
  \textbf{Name} & \textbf{Input} & \textbf{Output} & \textbf{Exceptions} \\
  \hline
  plot-stats & \{fitnessValues: int, generationTime: int, programCount: int, teamCount: int\} & \{PDF file\} & Returns a PDF file of plot statistics for an experiment \\
  \hline
  run-mpi & \{fitnessValues: int, generationTime: int, programCount: int, teamCount: int\} & \{OpenGL animation\} & An OpenGL animation starts to run \\
  \hline
  
  \end{tabular}
  
  \end{center}

\subsection{Semantics}

\subsubsection{State Variables}
N/A

\subsubsection{Environment Variables}

  \begin{center}
    \begin{tabular}{p{4cm} p{4cm} p{4cm}}
    \hline
    \textbf{Name} & \textbf{Type} & \textbf{Description} \\
    \hline
    tpg.[experimentId].std & File(s) & output log files generated for each experiment \\
    \hline
    \end{tabular}
    \end{center}

\subsubsection{Assumptions}

\begin{itemize}
  \item Format of the log files is known and will not change.
\end{itemize}
\subsubsection{Access Routine Semantics}

N/A

\subsubsection{Local Functions}

\begin{center}
  \begin{tabular}{p{3cm} p{3cm} p{3cm} p{4cm}}
  \hline
  \textbf{Name} & \textbf{Input} & \textbf{Output} & \textbf{Description} \\
  \hline
  extractMetrics & \{logFile: file\} & \{dataFile: file\} & Saves extracted data into .rslt files \\
  \hline
  transformData & \{logFile: file\} & \{dataFile: file\} & Reverse processes the log files, pattern matches, reformatting, and aggregating the data and saving to a .rslt file \\
  \hline
  plotData & \{logFile: file\} & \{plotFile: file\} & Plots the data from the .rslt file and saves the plot to a .pdf file \\
  \end{tabular}
\end{center}

\section{MIS of TPG Experiment Module} \label{TPGExperimentModule}

\subsection{Module}
TPGExperimentMPI

\subsection{Uses}
The TPG Experiment module is responsible for managing and evolving different policies, evaluating different tasks, and tracking experiments. It is used during the execution of experiments through the commands: \textbf{tpg-run-slurm} and \textbf{tpg-run-mpi}, which are used for executing tasks in virtual and local machines respectively.
\subsection{Syntax}

\subsubsection{Exported Constants}
None

\subsubsection{Exported Access Programs}
None

\subsection{Semantics}

\subsubsection{State Variables}
\begin{center}
  \begin{tabular}{p{4cm} p{3cm} p{7cm}}
  \hline
  \textbf{Name} & \textbf{Type} & \textbf{Description} \\
  \hline
  world\_rank & Integer & The rank of the MPI process within the environment. It is used to distinguish between the master and evaluator processes. \\
  \hline
  n\_task & Integer & The current number of tasks (environments) running. \\
  \hline
  active\_task & Integer & The index of the current active task. \\
  \hline
  phase & Integer & The numerical representation of the current phase of the program. \\
  \hline
  t\_current & Integer & The current generation or iteration of the task. \\
  \hline
  t\_start & Integer & The starting generation or iteration of the task. \\
  \hline
  task\_to\_replay & Integer & The index of the task to replay. \\
  \hline
  \end{tabular}
\end{center}

\subsubsection{Environment Variables}
\begin{center}
  \begin{tabular}{p{4cm} p{4cm} p{6cm}}
  \hline
  \textbf{Name} & \textbf{Type} & \textbf{Description} \\
  \hline
  COMET\_API\_KEY & String & The API key used for Comet experiment tracking service \\
  \hline
  \end{tabular}
  \end{center}

\subsubsection{Assumptions}
\begin{itemize}
  \item Experimental parameters such as \textbf{mj\_model\_path} and \textbf{active\_tasks} are well-defined. 
\end{itemize}

\subsubsection{Access Routine Semantics}
None

\subsubsection{Local Functions}
None

\newpage

\bibliographystyle {plainnat}
\bibliography {../../../refs/References}

\newpage

\section{Appendix} \label{Appendix}

\wss{Extra information if required}

\newpage{}

\section*{Appendix --- Reflection}

\wss{Not required for CAS 741 projects}

The information in this section will be used to evaluate the team members on the
graduate attribute of Problem Analysis and Design.

\input{../../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item Which of your design decisions stemmed from speaking to your client(s)
  or a proxy (e.g. your peers, stakeholders, potential users)? For those that
  were not, why, and where did they come from?
  \item While creating the design doc, what parts of your other documents (e.g.
  requirements, hazard analysis, etc), it any, needed to be changed, and why?
  \item What are the limitations of your solution?  Put another way, given
  unlimited resources, what could you do to make the project better? (LO\_ProbSolutions)
  \item Give a brief overview of other design solutions you considered.  What
  are the benefits and tradeoffs of those other designs compared with the chosen
  design?  From all the potential options, why did you select the documented design?
  (LO\_Explores)
\end{enumerate}


\end{document}